Poster: Online RL in the Programmable Dataplane with \approachshort{}

### 2021-10-18 paper/poster-abstract.tex
Terrible, terrible things.

% !TeX document-id = {5530719d-34df-4dd8-b4b5-e6ed092c2b36}
% !TeX program = pdflatex
% !BIB program = biber
\documentclass[
sigconf,natbib=false
,anonymous=true
]{acmart}

@@

% Copyright
%\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference info
%\setcopyright{none}
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

%\settopmatter{printacmref=false, printccs=false, printfolios=true}
\settopmatter{printfolios=true, printccs=true}
%\settopmatter{printacmref=false, printccs=true, printfolios=true}

% DOI
\acmDOI{12345}

% ISBN
\acmISBN{67890}

%Conference
\acmConference[CoNEXT '21]{the \nth{17} International COnference on emerging Networking EXperiments and Technologies}{December \numrange{7}{10}, 2021}{Online}
\acmYear{2021}
%\copyrightyear{}

%% {} with no args suppresses printing of the price
%\acmPrice{15.00}
\acmPrice{}

>>>>

% !TeX document-id = {5530719d-34df-4dd8-b4b5-e6ed092c2b36}
% !TeX program = pdflatex
% !BIB program = biber
\documentclass[
sigconf,natbib=false
%,anonymous=true
]{acmart}

@@

% Copyright
%\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference info
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

%\settopmatter{printacmref=false, printccs=false, printfolios=true}
%\settopmatter{printfolios=true, printccs=true}
%\settopmatter{printacmref=false, printccs=true, printfolios=true}

\acmYear{2021}
\copyrightyear{2021}
\setcopyright{acmcopyright}
\acmConference{CoNEXT '21}{December 7--10, 2021}{Virtual Event, Germany}
\acmPrice{TBA} % Use the data from your email from ACM rights management
\acmDOI{TBA} % Use the data from your email from ACM rights management
\acmISBN{TBA} % Use the data from your email from ACM rights management
